DSSynth: An Automated Synthesis Tool for Physical Plants \\ Digital Controllers via MATLAB Toolbox

### 2017-05-31 emsoft2017/emsoft-paper.tex
reviewed section 2.3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{itemize}
\item \textbf{Representation}: the synthesis could be performed for digital-systems in transfer-function or state-space equations;
\item \textbf{Fixed-Point Arithmetic}: the digital controller is synthesized considering FWL effects, in fixed-point numeric representation;
\item \textbf{Interface}: the synthesis could be executed using the command-line version, and a GUI Application version. In addition, in the GUI Application, the user is able to plot the step response in order to reproduce the stability of the digital controller synthesized;
\end{itemize}
%---------------------------------------------------
\subsection{\tool Usage}
%---------------------------------------------------

>>>>

\begin{itemize}
\item \textbf{Representation}: the synthesis can be performed for digital systems specified as transfer-function or state-space equations;
\item \textbf{Fixed-Point Arithmetic}: the digital controller is synthesized considering FWL effects, in fixed-point numeric representation;
\item \textbf{Interface}: the synthesis can be executed via command-line or graphical-user interface (GUI). For the GUI application, the user can plot the step response to reproduce the stability in closed-loop of the synthesized digital controller;
\end{itemize}
%---------------------------------------------------
\subsection{\tool Usage}
%---------------------------------------------------
